Approximate bayesian computation in large scale structure modeling : constraining the galaxy-halo connection

### 2016-01-21 halo/text/abc.tex

\documentclass[12pt, preprint]{aastex}
\usepackage[breaklinks,colorlinks, urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage{graphicx}	% For figures
\usepackage{natbib}	% For citep and citep
\usepackage{amsmath}	% for \iint
\usepackage{bm}
\usepackage[breaklinks]{hyperref}	% for blackboard bold numbers
\usepackage{hyperref}
\hypersetup{colorlinks}
\usepackage{color}
\usepackage{morefloats}
\definecolor{darkred}{rgb}{0.5,0,0}
\definecolor{darkgreen}{rgb}{0,0.5,0}
\definecolor{darkblue}{rgb}{0,0,0.5}
\hypersetup{ colorlinks,
linkcolor=darkblue,
filecolor=darkgreen,
urlcolor=darkred,
citecolor=darkblue}

@@

\subsection{Forward model of the large scale galaxy populations}\label{sec:halo}
\subsubsection{halo model}
Halo Occupation distribution is a powerful tool for description of galaxy/halo relation. \todo{Here we explain HOD modeling of galaxy positions, etc.}
\subsubsection{Generating mock galaxy populations with halotools}

\todo{Halotools allows us to forward model galaxy positions from HOD parameters. From the galaxy positions, we can calculate observable summary statistics such as the 2PCF, Group Multiplicity Function (GMF) and the number density $\bar{n}$.}

Talk about why it is better to simulate the mock and compute the summary statistics of the mock instead of 
using analytic formulas...

Talk about all the assumptions that go into analytic formulas...

Talk about why we do not want to write down likelihood function for gmf, 2pcf, ...
\subsubsection{summary statistics of galaxy populations}

@@

\todo{Talk about the observable: 2pcf, group multiplicity function, and number density ...}

\section{Mock data}\label{sec:data}

Plots showing 2pcf, gmf, ... of the mock data.
How we compute the covariance matrix from mocks...
Talk about error bars. Talk about poisson errors in group populations ...

@@

\todo{talk about why it is hard to do cosmology ...}

>>>>

\documentclass[12pt, preprint]{aastex}
\usepackage[breaklinks,colorlinks, urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage{graphicx}	% For figures
\usepackage{natbib}	% For citep and citep
\usepackage{amsmath}	% for \iint
\usepackage{bm}
\usepackage[breaklinks]{hyperref}	% for blackboard bold numbers
\usepackage{hyperref}
\usepackage{algorithmic,algorithm}
\hypersetup{colorlinks}
\usepackage{color}
\usepackage{morefloats}
\definecolor{darkred}{rgb}{0.5,0,0}
\definecolor{darkgreen}{rgb}{0,0.5,0}
\definecolor{darkblue}{rgb}{0,0,0.5}
\hypersetup{ colorlinks,
linkcolor=darkblue,
filecolor=darkgreen,
urlcolor=darkred,
citecolor=darkblue}

@@

\begin{algorithm}
\caption{The procedure for ABC-PMC}
\begin{algorithmic}[1]
%\STATE \DATA: D
%\STATE \RESULT: ABC posterior sample of $\pars$
\IF{$t=1:$}
%\STATE $\epsilon_t \gets \infty$
\FOR{$i=1,...,N$}
   \STATE // \emph{This loop can now be done in parallel for all i}
   \WHILE{$\rho(X,D)>\epsilon_t$}
   \STATE $\pars^{*}_{t} \gets \pi(\pars)$
   \STATE $X = f(\pars^{*}_{t})$
   \ENDWHILE
   \STATE $\pars^{(i)}_{t} \gets \pars^{*}_{t}$
   \STATE $w^{(i)}_{t} \gets 1/N$
\ENDFOR
\ENDIF
\IF{$t=2,...,T:$}
\FOR{$i=1,...,N$}
   \STATE // \emph{This loop can now be done in parallel for all i}
   \WHILE{$\rho(X,D)>\epsilon_t$}
   \STATE Draw $\pars^{*}_{t}$ from $\{\pars^{j}_{t-1}\}$ with probabilities $\{w^{j}_{t-1}\}$
   \STATE $\pars^{*}_{t} \gets K(\pars^{*}_{t},.)$
   \STATE $X = f(\pars^{*}_{t})$
   \ENDWHILE
   \STATE $\pars^{(i)}_{t} \gets \pars^{*}_{t}$
   \STATE $w^{(i)}_{t} \gets \frac{\pi(\pars^{(i)}_{t})}{\sum_{j=1}^{N}w_{t-1}^{(i)}K(\pars^{(j)}_{t-1},\pars^{(i)}_{t})}$
\ENDFOR
\ENDIF
\end{algorithmic}
\end{algorithm}

%\begin{algorithm}[H]
% \Data{this text}
% \Result{how to write algorithm with \LaTeX2e }
% initialization\;
% \While{not at end of this document}{
%  read current\;
%  \eIf{understand}{
%   go to next section\;
%   current section becomes this one\;
%   }{
%   go back to the beginning of current section\;
%  }
% }
% \caption{How to write algorithms}
%\end{algorithm}

\subsection{Forward model of the large scale galaxy populations}\label{sec:halo}
\subsubsection{halo model}
Dark matter halos are biased tracers of the underlying matter distribution of the universe. The halo model postulates that galaxies reside in dark matter halos. Halo Occupation distribution---HOD---is a powerful tool for description of galaxy--halo connection. HOD provides a probabilistic prescription for how galaxies populate halos. According to HOD modeling, the number of galaxies that populate a dark matter halo is dictated by the host halo mass $M_h$. The probability of a dark matter halo of mass $M_h$ being populated by $N_g$ galaxies---$P(N_g|M_h)$--- is a Poisson distribution, and is separable to two parts 
\beq
P(N_g|M_h) = P(N_\mathrm{cen}|M_h) + P(N_\mathrm{sat}|M_h),
\eeq
where $N_\mathrm{cen}$ is the number of central galaxies, and $N_\mathrm{sat}$ is the number of satellites.

\subsubsection{Generating mock galaxy populations with halotools}

%\todo{Halotools allows us to forward model galaxy positions from HOD parameters. From the galaxy positions, we can calculate observable summary statistics such as the 2PCF, Group Multiplicity Function (GMF) and the number density $\bar{n}$.}

%Talk about why it is better to simulate the mock and compute %the summary statistics of the mock instead of using analytic formulas...

%Talk about all the assumptions that go into analytic %formulas...

%Talk about why we do not want to write down likelihood %function for gmf, 2pcf, ...
\subsubsection{summary statistics of galaxy populations}

@@

%\todo{Talk about the observable: 2pcf, group multiplicity %function, and number density ...}

\section{Mock Observations}\label{sec:data}
\todo{The fake observations we use as "data" in our inference.}
%Plots showing 2pcf, gmf, ... of the mock data.
%How we compute the covariance matrix from mocks...
%Talk about error bars. Talk about poisson errors in group %populations ...

@@
